---
title: "Q2"
output: pdf_document
date: "2023-07-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ETAS.inlabru)
library(ggplot2)
library(extraDistr)
library(ggpubr)

# Increase num.cores if you have more cores on your computer, and reduce it
# if you have fewer!
num.cores <- 2

INLA::inla.setOption(num.threads = num.cores)
```

```{r}
generate_post.list<-function(true.param,true.beta,T1,T2,link.f,inv.link.f,th.init,itentifier){
  true.param <- true.param
  beta.p <- true.beta
  M0 <- 2.5
  T1 <- T1
  T2 <- T2
  # generate the catalogue - it returns a list of data.frames
  synth.cat.list <- generate_temporal_ETAS_synthetic(
    theta = true.param,
    beta.p = beta.p,
    M0 = M0,
    T1 = T1,
    T2 = T2,
    Ht = NULL,
    ncore = 1
  )
  synth.cat.df <- do.call(rbind, synth.cat.list)
  
  # set up list of bru options
  bru.opt.list <- list(
    bru_verbose = 0, # type of visual output
    bru_max_iter = 70, # maximum number of iterations
    # bru_method = list(max_step = 0.5),
    bru_initial = th.init
  ) # parameters initial values
  
  # sort catalogue by occurrence time
  synth.cat.df <- synth.cat.df[order(synth.cat.df$ts), ]
  # add event identifier
  synth.cat.df$idx.p <- seq_len(nrow(synth.cat.df))
  
  synth.fit <- Temporal.ETAS(
    total.data = synth.cat.df,
    M0 = M0,
    T1 = T1,
    T2 = T2,
    link.functions = link.f,
    coef.t. = 1,
    delta.t. = 0.1,
    N.max. = 5,
    bru.opt = bru.opt.list
  )
  
  # create input list to explore model output
  input_list <- list(
    model.fit = synth.fit,
    link.functions = link.f
  )
  
  post.list <- get_posterior_param(input.list = input_list)
  post.list$post.df$cat.used <- itentifier
  return(post.list)
}
```

```{r}
#fit the model on all parameters
set.seed(1)
true.param <- list(mu = 0.35, K = 0.15, alpha = 2.5, c = 0.1, p = 1.5)
true.beta <- 2.4
T1 <- 0
T2 <- 365

# set copula transformations list
link.f <- list(
  mu = \(x) gamma_t(x, 0.1, 0.1),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 1, 10)
)
  
# set inverse copula transformations list
inv.link.f <- list(
  mu = \(x) inv_gamma_t(x, 0.1, 0.1),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 1, 10)
)
  
# set up list of initial values
th.init <- list(
  th.mu = inv.link.f$mu(0.5),
  th.K = inv.link.f$K(0.1),
  th.alpha = inv.link.f$alpha(1),
  th.c = inv.link.f$c_(0.1),
  th.p = inv.link.f$p(1.1)
)

post.list_all<-generate_post.list(true.param,true.beta,T1,T2,link.f,inv.link.f,th.init,'all parameters')
```

```{r}
# create data.frame of true value of parameters
df.true.param <- data.frame(
  x = unlist(true.param),
  param = names(true.param)
)
# add to the marginal posterior distribution of the parameters the true value of the parameters.
post.list_all$post.plot +
  geom_vline(
    data = df.true.param,
    mapping = aes(xintercept = x), linetype = 2
  )
```

now try to fix all parameters on some values and see what's happening.

```{r}
#fixed on mu
set.seed(1)

# set copula transformations list
link.f_fix.on.mu <- list(
  mu = \(x) gamma_t(x, 0.35*10000, 10000),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 1, 10)
)
  
# set inverse copula transformations list
inv.link.f_fix.on.mu <- list(
  mu = \(x) inv_gamma_t(x, 0.35*10000, 10000),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 1, 10)
)

post.list_fix.on.mu<-generate_post.list(true.param,true.beta,T1,T2,
              link.f_fix.on.mu,inv.link.f_fix.on.mu,th.init,'fix on mu')
```

```{r}
#fixed on k
set.seed(1)

# set copula transformations list
link.f_fix.on.k <- list(
  mu = \(x) gamma_t(x, 0.1, 0.1),
  K = \(x) unif_t(x, 0.15, 0.15),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 1, 10)
)
  
# set inverse copula transformations list
inv.link.f_fix.on.k <- list(
  mu = \(x) inv_gamma_t(x, 0.1, 0.1),
  K = \(x) inv_unif_t(x, 0.15, 0.15),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 1, 10)
)

post.list_fix.on.k<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_fix.on.k,inv.link.f_fix.on.k,th.init,'fix on K')
```

```{r}
#fixed on alpha
set.seed(1)

# set copula transformations list
link.f_fix.on.alpha <- list(
  mu = \(x) gamma_t(x, 0.1, 0.1),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 2.5, 2.5),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 1, 10)
)
  
# set inverse copula transformations list
inv.link.f_fix.on.alpha <- list(
  mu = \(x) inv_gamma_t(x, 0.1, 0.1),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 2.5, 2.5),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 1, 10)
)

post.list_fix.on.alpha<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_fix.on.alpha,inv.link.f_fix.on.alpha,th.init,'fix on alpha')
```

```{r}
#fixed on c
set.seed(1)

# set copula transformations list
link.f_fix.on.c <- list(
  mu = \(x) gamma_t(x, 0.1, 0.1),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 0.1, 0.1),
  p = \(x) unif_t(x, 1, 10)
)
  
# set inverse copula transformations list
inv.link.f_fix.on.c <- list(
  mu = \(x) inv_gamma_t(x, 0.1, 0.1),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 0.1, 0.1),
  p = \(x) inv_unif_t(x, 1, 10)
)

post.list_fix.on.c<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_fix.on.c,inv.link.f_fix.on.c,th.init,'fix on c')
```

```{r}
#fixed on p
set.seed(1)

# set copula transformations list
link.f_fix.on.p <- list(
  mu = \(x) gamma_t(x, 0.1, 0.1),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 1.5, 1.5)
)
  
# set inverse copula transformations list
inv.link.f_fix.on.p <- list(
  mu = \(x) inv_gamma_t(x, 0.1, 0.1),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 1.5, 1.5)
)

post.list_fix.on.p<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_fix.on.p,inv.link.f_fix.on.p,th.init,'fix on p')
```

```{r}
# bind marginal posterior data.frames
bind.post <- rbind(post.list_all$post.df, post.list_fix.on.alpha$post.df,
                   post.list_fix.on.c$post.df, 
        post.list_fix.on.mu$post.df[!post.list_fix.on.mu$post.df$param=='mu',],
                   post.list_fix.on.k$post.df, post.list_fix.on.p$post.df)

ggplot(bind.post, aes(x = x, y = y, color = cat.used)) +
  geom_line() +
  facet_wrap(facets = ~param, scales = "free") +
  xlab("param") +
  ylab("pdf") +
  geom_vline(
    data = df.true.param,
    mapping = aes(xintercept = x), linetype = 2
  )
```

we can find some interesting conclusions: fix on K leads to a better estimation of alpha, fix on p leads to a better estimation of c, fix on alpha leads to a better estimation of K, fix on any other parameters cannot lead to a better estimate of mu, fix on c leads to a better estimation of p. So we can find that, K and alpha are highly correlated, p and c are highly correlated, any single parameter has little relationship to mu.

Now, explore how the combination of parameters can influence the estimate of other parameters.

mu & K, mu & alpha, mu & c, mu & p

K & alpha, K & c, K & p

alpha & c, alpha & p

c & p

```{r}
#fixed on mu & K
set.seed(1)

# set copula transformations list
link.f_fix.on.mu.k <- list(
  mu = \(x) gamma_t(x, 0.35*10000, 10000),
  K = \(x) unif_t(x, 0.15, 0.15),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 1, 10)
)
  
# set inverse copula transformations list
inv.link.f_fix.on.mu.k <- list(
  mu = \(x) inv_gamma_t(x, 0.35*10000, 10000),
  K = \(x) inv_unif_t(x, 0.15, 0.15),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 1, 10)
)

post.list_fix.on.mu.k<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_fix.on.mu.k,inv.link.f_fix.on.mu.k,th.init,'fix on mu & K')
```

```{r}
#fixed on mu & alpha
set.seed(1)

# set copula transformations list
link.f_fix.on.mu.alpha <- list(
  mu = \(x) gamma_t(x, 0.35*10000, 10000),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 2.5, 2.5),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 1, 10)
)
  
# set inverse copula transformations list
inv.link.f_fix.on.mu.alpha <- list(
  mu = \(x) inv_gamma_t(x, 0.35*10000, 10000),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 2.5, 2.5),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 1, 10)
)

post.list_fix.on.mu.alpha<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_fix.on.mu.alpha,inv.link.f_fix.on.mu.alpha,th.init,'fix on mu & alpha')
```

```{r}
#fixed on mu & c
set.seed(1)

# set copula transformations list
link.f_fix.on.mu.c <- list(
  mu = \(x) gamma_t(x, 0.35*10000, 10000),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 0.1, 0.1),
  p = \(x) unif_t(x, 1, 10)
)
  
# set inverse copula transformations list
inv.link.f_fix.on.mu.c <- list(
  mu = \(x) inv_gamma_t(x, 0.35*10000, 10000),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 0.1, 0.1),
  p = \(x) inv_unif_t(x, 1, 10)
)

post.list_fix.on.mu.c<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_fix.on.mu.c,inv.link.f_fix.on.mu.c,th.init,'fix on mu & c')
```

```{r}
#fixed on mu & p
set.seed(1)

# set copula transformations list
link.f_fix.on.mu.p <- list(
  mu = \(x) gamma_t(x, 0.35*10000, 10000),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 1.5, 1.5)
)
  
# set inverse copula transformations list
inv.link.f_fix.on.mu.p <- list(
  mu = \(x) inv_gamma_t(x, 0.35*10000, 10000),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 1,5, 1.5)
)

post.list_fix.on.mu.p<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_fix.on.mu.p,inv.link.f_fix.on.mu.p,th.init,'fix on mu & p')
```

```{r}
#fixed on K & alpha
set.seed(1)

# set copula transformations list
link.f_fix.on.k.alpha <- list(
  mu = \(x) gamma_t(x, 0.1, 0.1),
  K = \(x) unif_t(x, 0.15, 0.15),
  alpha = \(x) unif_t(x, 2.5, 2.5),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 1, 10)
)
  
# set inverse copula transformations list
inv.link.f_fix.on.k.alpha <- list(
  mu = \(x) inv_gamma_t(x, 0.1, 0.1),
  K = \(x) inv_unif_t(x, 0.15, 0.15),
  alpha = \(x) inv_unif_t(x, 2.5, 2.5),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 1, 10)
)

post.list_fix.on.k.alpha<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_fix.on.k.alpha,inv.link.f_fix.on.k.alpha,th.init,'fix on K & alpha')
```

```{r}
#fixed on K & c
set.seed(1)

# set copula transformations list
link.f_fix.on.k.c <- list(
  mu = \(x) gamma_t(x, 0.1, 0.1),
  K = \(x) unif_t(x, 0.15, 0.15),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 0.1, 0.1),
  p = \(x) unif_t(x, 1, 10)
)
  
# set inverse copula transformations list
inv.link.f_fix.on.k.c <- list(
  mu = \(x) inv_gamma_t(x, 0.1, 0.1),
  K = \(x) inv_unif_t(x, 0.15, 0.15),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 0.1, 0.1),
  p = \(x) inv_unif_t(x, 1, 10)
)

post.list_fix.on.K.c<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_fix.on.k.c,inv.link.f_fix.on.k.c,th.init,'fix on K & c')
```

```{r}
#fixed on K & p
set.seed(1)

# set copula transformations list
link.f_fix.on.k.p <- list(
  mu = \(x) gamma_t(x, 0.1, 0.1),
  K = \(x) unif_t(x, 0.15, 0.15),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 1.5, 1.5)
)
  
# set inverse copula transformations list
inv.link.f_fix.on.k.p <- list(
  mu = \(x) inv_gamma_t(x, 0.1, 0.1),
  K = \(x) inv_unif_t(x, 0.15, 0.15),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 1.5, 1.5)
)

post.list_fix.on.K.p<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_fix.on.k.p,inv.link.f_fix.on.k.p,th.init,'fix on K & p')
```

```{r}
#fixed on alpha & c
set.seed(1)

# set copula transformations list
link.f_fix.on.alpha.c <- list(
  mu = \(x) gamma_t(x, 0.1, 0.1),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 2.5, 2.5),
  c_ = \(x) unif_t(x, 0.1, 0.1),
  p = \(x) unif_t(x, 1, 10)
)
  
# set inverse copula transformations list
inv.link.f_fix.on.alpha.c <- list(
  mu = \(x) inv_gamma_t(x, 0.1, 0.1),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 2.5, 2.5),
  c_ = \(x) inv_unif_t(x, 0.1, 0.1),
  p = \(x) inv_unif_t(x, 1, 10)
)

post.list_fix.on.alpha.c<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_fix.on.alpha.c,inv.link.f_fix.on.alpha.c,th.init,'fix on alpha & c')
```

```{r}
#fixed on alpha & p
set.seed(1)

# set copula transformations list
link.f_fix.on.alpha.p <- list(
  mu = \(x) gamma_t(x, 0.1, 0.1),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 2.5, 2.5),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 1.5, 1.5)
)
  
# set inverse copula transformations list
inv.link.f_fix.on.alpha.p <- list(
  mu = \(x) inv_gamma_t(x, 0.1, 0.1),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 2.5, 2.5),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 1.5, 1.5)
)

post.list_fix.on.alpha.p<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_fix.on.alpha.p,inv.link.f_fix.on.alpha.p,th.init,'fix on alpha & p')
```

```{r}
#fixed on c & p
set.seed(1)

# set copula transformations list
link.f_fix.on.c.p <- list(
  mu = \(x) gamma_t(x, 0.1, 0.1),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 0.1, 0.1),
  p = \(x) unif_t(x, 1.5, 1.5)
)
  
# set inverse copula transformations list
inv.link.f_fix.on.c.p <- list(
  mu = \(x) inv_gamma_t(x, 0.1, 0.1),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 0.1, 0.1),
  p = \(x) inv_unif_t(x, 1.5, 1.5)
)

post.list_fix.on.c.p<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_fix.on.c.p,inv.link.f_fix.on.c.p,th.init,'fix on c & p')
```

```{r}
# bind marginal posterior data.frames
bind.post.two <- rbind(
  post.list_all$post.df, 
  post.list_fix.on.mu.alpha$post.df[!(post.list_fix.on.mu.alpha$post.df$param
                   =='mu'|post.list_fix.on.mu.alpha$post.df$param=='alpha'),],
  post.list_fix.on.mu.c$post.df[!(post.list_fix.on.mu.alpha$post.df$param
                   =='mu'|post.list_fix.on.mu.alpha$post.df$param=='c'),], 
  post.list_fix.on.mu.k$post.df[!(post.list_fix.on.mu.alpha$post.df$param
                   =='mu'|post.list_fix.on.mu.alpha$post.df$param=='K'),],
  post.list_fix.on.mu.p$post.df[!(post.list_fix.on.mu.alpha$post.df$param
                   =='mu'|post.list_fix.on.mu.alpha$post.df$param=='p'),], 
  post.list_fix.on.k.alpha$post.df[!(post.list_fix.on.mu.alpha$post.df$param
                   =='K'|post.list_fix.on.mu.alpha$post.df$param=='alpha'),],
  post.list_fix.on.K.c$post.df[!(post.list_fix.on.mu.alpha$post.df$param
                   =='K'|post.list_fix.on.mu.alpha$post.df$param=='c'),],  
  post.list_fix.on.K.p$post.df[!(post.list_fix.on.mu.alpha$post.df$param
                   =='K'|post.list_fix.on.mu.alpha$post.df$param=='p'),],
  post.list_fix.on.alpha.c$post.df[!(post.list_fix.on.mu.alpha$post.df$param
                   =='alpha'|post.list_fix.on.mu.alpha$post.df$param=='c'),], 
  post.list_fix.on.alpha.p$post.df[!(post.list_fix.on.mu.alpha$post.df$param
                   =='alpha'|post.list_fix.on.mu.alpha$post.df$param=='p'),],
  post.list_fix.on.c.p$post.df[!(post.list_fix.on.mu.alpha$post.df$param
                   =='c'|post.list_fix.on.mu.alpha$post.df$param=='p'),])

ggplot(bind.post.two, aes(x = x, y = y, color = cat.used)) +
  geom_line() +
  facet_wrap(facets = ~param, scales = "free") +
  xlab("param") +
  ylab("pdf") +
  geom_vline(
    data = df.true.param,
    mapping = aes(xintercept = x), linetype = 2
  )
```

From the plots above, we can see that the estimate of mu will always be stable.

Now, explore the effect of mis-specifying some of the parameters. It's known that p and c, K and alpha can help each other get better estimate, so mis-specify them and see what will happen.

```{r}
#mis-specify p to 5
set.seed(1)

# set copula transformations list
link.f_mis.p <- list(
  mu = \(x) gamma_t(x, 0.1, 0.1),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 5, 5)
)
  
# set inverse copula transformations list
inv.link.f_mis.p <- list(
  mu = \(x) inv_gamma_t(x, 0.1, 0.1),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 5, 5)
)

post.list_mis.p<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_mis.p,inv.link.f_mis.p,th.init,'mis-specify p')
```

```{r}
#mis-specify c to 2
set.seed(1)

# set copula transformations list
link.f_mis.c <- list(
  mu = \(x) gamma_t(x, 0.1, 0.1),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 2, 2),
  p = \(x) unif_t(x, 1, 10)
)
  
# set inverse copula transformations list
inv.link.f_mis.c <- list(
  mu = \(x) inv_gamma_t(x, 0.1, 0.1),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 2, 2),
  p = \(x) inv_unif_t(x, 1, 10)
)

post.list_mis.c<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_mis.c,inv.link.f_mis.c,th.init,'mis-specify c')
```

```{r}
#mis-specify K to 1.5
set.seed(1)

# set copula transformations list
link.f_mis.k <- list(
  mu = \(x) gamma_t(x, 0.1, 0.1),
  K = \(x) unif_t(x, 1.5, 1.5),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 1, 10)
)
  
# set inverse copula transformations list
inv.link.f_mis.k <- list(
  mu = \(x) inv_gamma_t(x, 0.1, 0.1),
  K = \(x) inv_unif_t(x, 1.5, 1.5),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 1, 10)
)

post.list_mis.k<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_mis.k,inv.link.f_mis.k,th.init,'mis-specify K')
```

```{r}
#mis-specify alpha to 8
set.seed(1)

# set copula transformations list
link.f_mis.alpha <- list(
  mu = \(x) gamma_t(x, 0.1, 0.1),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 8, 8),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 1, 10)
)
  
# set inverse copula transformations list
inv.link.f_mis.alpha <- list(
  mu = \(x) inv_gamma_t(x, 0.1, 0.1),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 8, 8),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 1, 10)
)

post.list_mis.alpha<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_mis.alpha,inv.link.f_mis.alpha,th.init,'mis-specify alpha')
```

```{r}
#mis-specify mu to 0.7
set.seed(1)

# set copula transformations list
link.f_mis.mu <- list(
  mu = \(x) gamma_t(x, 0.7*10000, 10000),
  K = \(x) unif_t(x, 0, 10),
  alpha = \(x) unif_t(x, 0, 10),
  c_ = \(x) unif_t(x, 0, 10),
  p = \(x) unif_t(x, 1, 10)
)
  
# set inverse copula transformations list
inv.link.f_mis.mu <- list(
  mu = \(x) inv_gamma_t(x, 0.7*10000, 10000),
  K = \(x) inv_unif_t(x, 0, 10),
  alpha = \(x) inv_unif_t(x, 0, 10),
  c_ = \(x) inv_unif_t(x, 0, 10),
  p = \(x) inv_unif_t(x, 1, 10)
)

post.list_mis.mu<-generate_post.list(true.param,true.beta,T1,T2,
  link.f_mis.mu,inv.link.f_mis.mu,th.init,'mis-specify mu')
```

```{r}
#difference bewteen the estimate of alpha by mis-specifying mu,c,p and k
bind.post.mis.alpha.g1 <- rbind(post.list_all$post.df, post.list_mis.p$post.df,
                       post.list_mis.c$post.df,post.list_mis.mu$post.df)
bind.post.mis.alpha.g2 <- rbind(post.list_all$post.df, post.list_mis.k$post.df)

post.df.mis.alpha.g1<-bind.post.mis.alpha.g1[bind.post.mis.alpha.g1$param=='alpha',]
post.df.mis.alpha.g2<-bind.post.mis.alpha.g2[bind.post.mis.alpha.g2$param=='alpha',]

gg1<-ggplot(post.df.mis.alpha.g1, aes(x = x, y = y, color = cat.used)) +
  geom_line() +
  facet_wrap(facets = ~param, scales = "free") +
  xlab("param") +
  ylab("pdf") +
  geom_vline(
    data = data.frame(x = 2.5,param = 'alpha'),
    mapping = aes(xintercept = x), linetype = 2
  )

gg2<-ggplot(post.df.mis.alpha.g2, aes(x = x, y = y, color = cat.used)) +
  geom_line() +
  facet_wrap(facets = ~param, scales = "free") +
  xlab("param") +
  ylab("pdf") +
  geom_vline(
    data = data.frame(x = 2.5,param = 'alpha'),
    mapping = aes(xintercept = x), linetype = 2
  )

ggarrange(gg1,gg2,ncol=1,nrow=2,align='hv')
```

```{r}
#difference bewteen the estimate of k by mis-specifying mu,c,p and alpha
bind.post.mis.k.g1 <- rbind(post.list_all$post.df, post.list_mis.p$post.df,
                       post.list_mis.c$post.df,post.list_mis.mu$post.df)
bind.post.mis.k.g2 <- rbind(post.list_all$post.df, post.list_mis.alpha$post.df)

post.df.mis.k.g1<-bind.post.mis.k.g1[bind.post.mis.k.g1$param=='K',]
post.df.mis.k.g2<-bind.post.mis.k.g2[bind.post.mis.k.g2$param=='K',]

gg1<-ggplot(post.df.mis.k.g1, aes(x = x, y = y, color = cat.used)) +
  geom_line() +
  facet_wrap(facets = ~param, scales = "free") +
  xlab("param") +
  ylab("pdf") +
  geom_vline(
    data = data.frame(x = 0.15,param = 'K'),
    mapping = aes(xintercept = x), linetype = 2
  )

gg2<-ggplot(post.df.mis.k.g2, aes(x = x, y = y, color = cat.used)) +
  geom_line() +
  facet_wrap(facets = ~param, scales = "free") +
  xlab("param") +
  ylab("pdf") +
  geom_vline(
    data = data.frame(x = 0.15,param = 'K'),
    mapping = aes(xintercept = x), linetype = 2
  )

ggarrange(gg1,gg2,ncol=1,nrow=2,align='hv')
```

```{r}
#difference bewteen the estimate of c by mis-specifying mu,alpha,k and p
bind.post.mis.c.g1 <- rbind(post.list_all$post.df, post.list_mis.alpha$post.df,
                       post.list_mis.k$post.df,post.list_mis.mu$post.df)
bind.post.mis.c.g2 <- rbind(post.list_all$post.df, post.list_mis.p$post.df)

post.df.mis.c.g1<-bind.post.mis.c.g1[bind.post.mis.c.g1$param=='c',]
post.df.mis.c.g2<-bind.post.mis.c.g2[bind.post.mis.c.g2$param=='c',]

gg1<-ggplot(post.df.mis.c.g1, aes(x = x, y = y, color = cat.used)) +
  geom_line() +
  facet_wrap(facets = ~param, scales = "free") +
  xlab("param") +
  ylab("pdf") +
  geom_vline(
    data = data.frame(x = 0.1,param = 'c'),
    mapping = aes(xintercept = x), linetype = 2
  )

gg2<-ggplot(post.df.mis.c.g2, aes(x = x, y = y, color = cat.used)) +
  geom_line() +
  facet_wrap(facets = ~param, scales = "free") +
  xlab("param") +
  ylab("pdf") +
  geom_vline(
    data = data.frame(x = 0.1,param = 'c'),
    mapping = aes(xintercept = x), linetype = 2
  )

ggarrange(gg1,gg2,ncol=1,nrow=2,align='hv')
```

```{r}
#difference bewteen the estimate of p by mis-specifying mu,alpha,k and c
bind.post.mis.p.g1 <- rbind(post.list_all$post.df, post.list_mis.alpha$post.df,
                       post.list_mis.k$post.df,post.list_mis.mu$post.df)
bind.post.mis.p.g2 <- rbind(post.list_all$post.df, post.list_mis.c$post.df)

post.df.mis.p.g1<-bind.post.mis.p.g1[bind.post.mis.p.g1$param=='p',]
post.df.mis.p.g2<-bind.post.mis.p.g2[bind.post.mis.p.g2$param=='p',]

gg1<-ggplot(post.df.mis.p.g1, aes(x = x, y = y, color = cat.used)) +
  geom_line() +
  facet_wrap(facets = ~param, scales = "free") +
  xlab("param") +
  ylab("pdf") +
  geom_vline(
    data = data.frame(x = 1.5,param = 'p'),
    mapping = aes(xintercept = x), linetype = 2
  )

gg2<-ggplot(post.df.mis.p.g2, aes(x = x, y = y, color = cat.used)) +
  geom_line() +
  facet_wrap(facets = ~param, scales = "free") +
  xlab("param") +
  ylab("pdf") +
  geom_vline(
    data = data.frame(x = 1.5,param = 'p'),
    mapping = aes(xintercept = x), linetype = 2
  )

ggarrange(gg1,gg2,ncol=1,nrow=2,align='hv')
```

```{r}
#difference bewteen the estimate of p by mis-specifying mu,alpha,k and c
bind.post.mis.mu <- rbind(post.list_all$post.df, post.list_mis.alpha$post.df,
                       post.list_mis.k$post.df,post.list_mis.c$post.df,
                       post.list_mis.p$post.df)

post.df.mis.mu<-bind.post.mis.mu[bind.post.mis.mu$param=='mu',]

ggplot(post.df.mis.mu, aes(x = x, y = y, color = cat.used)) +
  geom_line() +
  facet_wrap(facets = ~param, scales = "free") +
  xlab("param") +
  ylab("pdf") +
  geom_vline(
    data = data.frame(x = 0.35,param = 'mu'),
    mapping = aes(xintercept = x), linetype = 2
  )
```

```{r}
# bind marginal posterior data.frames
bind.post.mis <- rbind(post.list_all$post.df, post.list_mis.p$post.df,
                   post.list_mis.c$post.df, post.list_mis.k$post.df, 
                   post.list_mis.alpha$post.df,
                  post.list_mis.mu$post.df[!post.list_mis.mu$post.df$param=='mu',])

ggplot(bind.post.mis, aes(x = x, y = y, color = cat.used)) +
  geom_line() +
  facet_wrap(facets = ~param, scales = "free") +
  xlab("param") +
  ylab("pdf") +
  geom_vline(
    data = df.true.param,
    mapping = aes(xintercept = x), linetype = 2
  )
```

Generally speaking, when mis-specifying K, all estimation of other parameters get worse, when mis-specifying p (or c), estimate of c (or p) will get worse, when mis-specifying alpha, estimate of K will get worse.
